---
title: "Developing Data Products Assignment"
author: "Kapil Kumar Kaushik"
date: "October 12, 2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Project Detail

A simple shiny application that has been built and published to generate the linear regression between two variables the of "matcars" dataset.

In this application , the user choose the predictor and outcome is always fixed as "mpg".

Appliation can be viewed at :

- Shiny Server link : 
    https://kapil-kaushik.shinyapps.io/Shiny_Project/
- GitHub repo : 
    https://github.com/kapilkaushik2/DataProducts

## Summary of dataset

The data was extracted from the 1974 Motor Trend US magazine and comprises fuel consumption and 10 aspects of automobile design and performance of 32 automobiles.

The mtcars dataset has 32 entried with 11 columns as follows:
```{r cars, echo = TRUE , comment=""}
head(mtcars)
```

## How it works

- The user select the predictor.
- The user select a color of the regression line.
- When the user provide the values , plot is updated.
- It also shows the summary of the predicted variable selected.

## Thanks

